---
title: "Demonstration 4"
author: "Nnenna Asidianya"
date: "8/3/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,warning=FALSE)
```

For demonstration purposes I have displayed the code, hence echo=TRUE here. For your final report please do not show the code in the write up. 

## Creating tables in R

```{r}

#set your own WD; this is mine to the buses file
setwd("C:/Users/User/Desktop/STA302 Summer/Week 3/Lecture 5")

buses=read.table('buses.txt', header=FALSE)
colnames(buses) <- c("expense","miles", "percentD", "percentF", "receipt")
attach(buses)

```
### Gtsummary Table:

```{r}
#install.packages("gtsummary")
library(gtsummary)

multi.fit = glm(expense~ miles + percentD, data=buses)


t1 <- tbl_regression(multi.fit, exponentiate = FALSE)
t1
```


For more information: http://www.danieldsjoberg.com/gtsummary/

### ktable:

```{r}
library(kableExtra)

beta<-c("beta1", "beta2","beta3")
value<-c(1, 2.1, 0.5)

#basic
dt<-data.frame(beta, value)
tbl<-kbl(dt)
tbl
```
For more information:  
https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html  

You can do more with ktable, so search about the link I have provided. 

## Report Formatting:

A built in math mode to write out your regression models:

$$y_i = b_0 + b_1 x_i + \epsilon$$
For creating subection headers:

# Header

## Header 2

### Header 3

https://rmarkdown.rstudio.com/authoring_basics.html 


