---
title: "FinalReport"
author: "Gautam Gireesh, Saakshi Shah"
date: "22/08/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

As aspiring statisticians, the goal of this study for us was to develop a reasonable regression model using the techniques we have learnt over the course of this semester. Through this, we would be able to understand and determine what factors do in fact impact a student's performance on quiz 4. At a glance, it would be easy for us to assume that all the aspects - country, quiz grades, hours spent on COVID and stats - must make an impact. But having been students of this course, we know better and will put our intuition to the test to determine whether or not all the factors make an impact. The following report will conduct an in-depth analysis of the data and explain how and why we chose the model.

```{r, include=FALSE}
library(tidyverse)
library(olsrr)
library(rcompanion)
library(caret)
library(ggplot2)
df<-read.csv("new_Data.csv")
data_split<-split(df, df$Country)
american_data<-rbind(data_split$Canada, data_split$USA)
asian_data<-rbind(data_split$China, data_split$India, data_split$Mongolia, data_split$Pakistan, data_split$Singapore, data_split$`South Korea`, data_split$Taiwan, data_split$UAE)
```

```{r covid hours AMERICAN}
covid1 = american_data[,c(3)]
covid2 = american_data[,c(7)]
covid3 = american_data[,c(10)]
covid4 = american_data[,c(13)]

covid_list<-list(covid1, covid2, covid3, covid4)
covid_matrice<-do.call(cbind, covid_list)
covid_average<-rowMeans(covid_matrice, na.rm = TRUE)
covid_mean<-mean(covid_average, na.rm = TRUE)
centered_covid_avg<-covid_average - covid_mean
american_covid <- hist(centered_covid_avg)
```

```{r covid hours ASIAN}
asian_covid1 = asian_data[,c(3)]
asian_covid2 = asian_data[,c(7)]
asian_covid3 = asian_data[,c(10)]
asian_covid4 = asian_data[,c(13)]

asian_covid_list<-list(asian_covid1, asian_covid2, asian_covid3, asian_covid4)
asian_covid_matrice<-do.call(cbind, asian_covid_list)
asian_covid_average<-rowMeans(asian_covid_matrice, na.rm = TRUE)
asian_covid_mean<-mean(asian_covid_average, na.rm = TRUE)
asian_centered_covid_avg<-asian_covid_average - asian_covid_mean
asian_covid <- hist(asian_centered_covid_avg)
```

```{r quiz score AMERICAN}
quiz1 = american_data[,c(5)]
quiz2 = american_data[,c(8)]
quiz3 = american_data[,c(11)]
quiz4 = american_data[,c(14)]
hist(quiz4)

quiz_list<-list(quiz1, quiz2, quiz3)
quiz_matrice<-do.call(cbind, quiz_list)
quiz_average<-rowMeans(quiz_matrice, na.rm = TRUE)
quiz_mean<-mean(quiz_average, na.rm = TRUE)
centered_quiz_avg<-quiz_average - quiz_mean
american_quiz <- hist(centered_quiz_avg)
```

```{r quiz score ASIAN}
asian_quiz1 = asian_data[,c(5)]
asian_quiz2 = asian_data[,c(8)]
asian_quiz3 = asian_data[,c(11)]
asian_quiz4 = asian_data[,c(14)]

asian_quiz_list<-list(asian_quiz1, asian_quiz2, asian_quiz3)
asian_quiz_matrice<-do.call(cbind, asian_quiz_list)
asian_quiz_average<-rowMeans(asian_quiz_matrice, na.rm = TRUE)
asian_quiz_mean<-mean(asian_quiz_average, na.rm = TRUE)
asian_centered_quiz_avg<-asian_quiz_average - asian_quiz_mean
asian_quiz <- hist(asian_centered_quiz_avg)
```

```{r stats hours AMERICAN}
sta1 = american_data[,c(2)]
sta2 = american_data[,c(6)]
sta3 = american_data[,c(9)]
sta4 = american_data[,c(12)]

sta_list<-list(sta1, sta2, sta3, sta4)
sta_matrice<-do.call(cbind, sta_list)
sta_average<-rowMeans(sta_matrice, na.rm = TRUE)
sta_mean<-mean(sta_average, na.rm = TRUE)
centered_sta_avg<-sta_average - sta_mean
american_stats <- hist(centered_sta_avg)
```

```{r stats hours ASIAN}
asian_sta1 = asian_data[,c(2)]
asian_sta2 = asian_data[,c(6)]
asian_sta3 = asian_data[,c(9)]
asian_sta4 = asian_data[,c(12)]

asian_sta_list<-list(asian_sta1, asian_sta2, asian_sta3, asian_sta4)
asian_sta_matrice<-do.call(cbind, asian_sta_list)
asian_sta_average<-rowMeans(asian_sta_matrice, na.rm = TRUE)
asian_sta_mean<-mean(asian_sta_average, na.rm = TRUE)
asian_centered_sta_avg<-asian_sta_average - asian_sta_mean
asian_stats <- hist(asian_centered_sta_avg)
```



```{r constructing final data frame}
X <- data.frame(centered_covid_avg, centered_sta_avg, centered_quiz_avg)
Y <- data.frame(quiz4)
```

```{r Analyzing relation between response and explanatory variables AMERICAN}
pairs(~centered_covid_avg + centered_sta_avg + centered_quiz_avg, data = X)
pairs(~asian_centered_covid_avg + asian_centered_sta_avg + asian_centered_quiz_avg, data = X)
```



## Choice of Method


## Variable Selection


## Description of Data


## Processing of Obtaining Final Model


## Goodness of Final Model


## Final Model Interpretation and Importance:


## Limitations of Analysis:

## Appendix

### American Dataset modelling

```{r echo=TRUE, results = 'hide'}
n<-length(quiz4)

full_model<-lm(quiz4 ~ centered_covid_avg + centered_sta_avg + centered_quiz_avg, data=american_data)

model1<-lm(quiz4~centered_covid_avg, data=american_data)
p_prime1 <- length(model1$coefficients)
summary(model1)
SSres1<-deviance(model1)
AIC1<-n*log(SSres1) -n*log(n) + 2*p_prime1
print(AIC1)
mallow_cp1<-ols_mallows_cp(model1, full_model)

model2<-lm(quiz4~centered_sta_avg, data=american_data)
p_prime2 <- length(model2$coefficients)
summary(model2)
SSres2<-deviance(model2)
AIC2<-n*log(SSres2) -n*log(n) + 2*p_prime2
print(AIC2)
mallow_cp2<-ols_mallows_cp(model2, full_model)

model3<-lm(quiz4~centered_quiz_avg, data=american_data)
p_prime3 <- length(model3$coefficients)
summary(model3)
SSres3<-deviance(model3)
AIC3<-n*log(SSres3) -n*log(n) + 2*p_prime3
print(AIC3)
mallow_cp3<-ols_mallows_cp(model3, full_model)
layout(matrix(c(1,2,3,4),2,2))
plot(model3)

model4<-lm(quiz4~centered_covid_avg + centered_quiz_avg, data=american_data)
p_prime4 <- length(model4$coefficients)
summary(model4)
SSres4<-deviance(model4)
AIC4<-n*log(SSres4) -n*log(n) + 2*p_prime4
print(AIC4)
mallow_cp4<-ols_mallows_cp(model4, full_model)

model5<-lm(quiz4~centered_sta_avg + centered_quiz_avg, data=american_data)
p_prime5 <- length(model5$coefficients)
summary(model5)
ssres5<-deviance(model5)
aic5<-n*log(ssres5) -n*log(n) + 2*p_prime5
print(aic5)
mallow_cp5<-ols_mallows_cp(model5, full_model)


model6<-lm(quiz4~centered_sta_avg + centered_covid_avg, data=american_data)
p_prime6 <- length(model6$coefficients)
summary(model6)
SSres6<-deviance(model6)
AIC6<-n*log(SSres6) -n*log(n) + 2*p_prime6
print(AIC6)
mallow_cp6<-ols_mallows_cp(model6, full_model)

model7<-lm(quiz4~centered_quiz_avg + centered_covid_avg + centered_sta_avg, data=american_data)
p_prime7 <- length(model7$coefficients)
summary(model7)
SSres7<-deviance(model7)
AIC7<-n*log(SSres7) -n*log(n) + 2*p_prime7
print(AIC7)
mallow_cp7<-ols_mallows_cp(model7, full_model)
```

### Asian Dataset modelling

```{r echo=TRUE, results = 'hide'}
asian_n<-length(asian_quiz4)

asian_full_model<-lm(asian_quiz4~asian_centered_covid_avg + asian_centered_sta_avg + asian_centered_quiz_avg, data=asian_data)

asian_model1<-lm(asian_quiz4~asian_centered_covid_avg, data=asian_data)
asian_p_prime1 <- length(asian_model1$coefficients)
summary(asian_model1)
asian_SSres1<-deviance(asian_model1)
asian_AIC1<-asian_n*log(asian_SSres1) -asian_n*log(asian_n) + 2*asian_p_prime1
print(asian_AIC1)
asian_mallow_cp1<-ols_mallows_cp(asian_model1, asian_full_model)

asian_model2<-lm(asian_quiz4~asian_centered_sta_avg, data=asian_data)
asian_p_prime2 <- length(asian_model2$coefficients)
summary(asian_model2)
asian_SSres2<-deviance(asian_model2)
asian_AIC2<-asian_n*log(asian_SSres2) -asian_n*log(asian_n) + 2*asian_p_prime2
print(asian_AIC2)
asian_mallow_cp2<-ols_mallows_cp(asian_model2, asian_full_model)

asian_model3<-lm(asian_quiz4~asian_centered_quiz_avg, data=asian_data)
asian_p_prime3 <- length(asian_model3$coefficients)
summary(asian_model3)
asian_SSres3<-deviance(asian_model3)
asian_AIC3<-asian_n*log(asian_SSres3) -asian_n*log(asian_n) + 2*asian_p_prime3
print(asian_AIC3)
asian_mallow_cp3<-ols_mallows_cp(asian_model3, asian_full_model)

asian_model4<-lm(asian_quiz4~asian_centered_covid_avg + asian_centered_quiz_avg, data=asian_data)
asian_p_prime4 <- length(asian_model4$coefficients)
summary(asian_model4)
asian_SSres4<-deviance(asian_model4)
asian_AIC4<-asian_n*log(asian_SSres4) -asian_n*log(asian_n) + 2*asian_p_prime4
print(asian_AIC4)
asian_mallow_cp4<-ols_mallows_cp(asian_model4, asian_full_model)

asian_model5<-lm(asian_quiz4~asian_centered_sta_avg + asian_centered_quiz_avg, data=asian_data)
asian_p_prime5 <- length(asian_model5$coefficients)
summary(asian_model5)
asian_SSres5<-deviance(asian_model5)
asian_AIC5<-asian_n*log(asian_SSres5) -asian_n*log(asian_n) + 2*asian_p_prime5
print(asian_AIC5)
asian_mallow_cp5<-ols_mallows_cp(asian_model5, asian_full_model)
layout(matrix(c(1,2,3,4),2,2))
plot(asian_model5)

asian_model6<-lm(asian_quiz4~asian_centered_sta_avg + asian_centered_covid_avg, data=asian_data)
asian_p_prime6 <- length(asian_model6$coefficients)
summary(asian_model6)
asian_SSres6<-deviance(asian_model6)
asian_AIC6<-asian_n*log(asian_SSres6) -asian_n*log(asian_n) + 2*asian_p_prime6
print(asian_AIC6)
asian_mallow_cp6<-ols_mallows_cp(asian_model6, asian_full_model)

asian_model7<-lm(asian_quiz4~asian_centered_quiz_avg + asian_centered_covid_avg + asian_centered_sta_avg, data=asian_data)
asian_p_prime7 <- length(asian_model7$coefficients)
summary(asian_model7)
asian_SSres7<-deviance(asian_model7)
asian_AIC7<-asian_n*log(asian_SSres7) -asian_n*log(asian_n) + 2*asian_p_prime7
print(asian_AIC7)
asian_mallow_cp7<-ols_mallows_cp(asian_model7, asian_full_model)
```

